A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-15 mt-marathon.2013/PBML_article.tex

Firstly, in Moses and cdec, the calculation of language model state is delegated to the language model implementation~\cite{Heafield-left} which uses the internal data-structure of the language model to determine state (??? Ney paper from yrs ago). Joshua, on the other hand, uses the words in the left and right context to determine language model state. This results in more aggressive hypothesis recombination in Moses and cdec, leading to better model score.

Secondly, the glue rule formulation in Moses and cdec is different from Joshua's. In Moses and cdec, the glue rule grammar is:
\begin{verbatim}
   S -> <s>
   S -> S X
   GOAL -> S </s> 
\end{verbatim}
where <s> and </s> are first-class words like any other. In Joshua, the glue rule grammar is:
\begin{verbatim}
   S -> X
   S -> S X
   GOAL -> <s> S </s> 
\end{verbatim}
In Moses and cdec formulation, glued hypotheses know that they are bound to the beginning of sentence <s>.  Therefore, their left language model state is empty and more hypotheses can recombine.  This is better than Joshua, where hypotheses are informed about <s> and </s> only after forming a complete sentence, so the left states are spuriously ambiguous.  Moreover, hypothesis score estimates are more accurate when they know about <s> earlier. Figure~\ref{fig:glue} shows the improvement in cdec by changing the glue rule formulation. This improvement was the direct result of research comparing the three decoders.

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.50]{glue.pdf}
\end{center}
\caption{Affect on model score by changing glue-rule formulation}
\label{fig:glue}
\end{figure}

>>>>

This is likely due to the fact that in Moses and cdec, the calculation of language model state is delegated to the language model implementation~\cite{Heafield-left} which uses the internal data-structure of the language model to determine state. Joshua, on the other hand, uses the words in the left and right context to determine language model state. This results in more aggressive hypothesis recombination in Moses and cdec, leading to better model score. Joshua will soon be updated~\footnote{\url{https://github.com/hieuhoang/papers/commit/e417a6adcf4f1e49954836b14799509fecdea11c#mt-marathon.2013} } to incorporate better left-state minimisation to match the perform of Moses and cdec.

\subsection{Glue Rules}

The glue rule formulation in Moses and cdec is different from Joshua's. In Moses and cdec, the glue rule grammar is:
 \begin{verbatim}
    S -> <s>
    S -> S X
    GOAL -> S </s> 
 \end{verbatim}
 where <s> and </s> are first-class words like any other. In Joshua, the glue rule grammar is:
 \begin{verbatim}
    S -> X
    S -> S X
    GOAL -> <s> S </s> 
 \end{verbatim}
 In Moses and cdec formulation, glued hypotheses know that they are bound to the beginning of sentence <s>.  Therefore, their left language model state is empty and more hypotheses can recombine.  This is better than Joshua, where hypotheses are informed about <s> and </s> only after forming a complete sentence, so the left states are spuriously ambiguous.  Moreover, hypothesis score estimates are more accurate when they know about <s> earlier. Figure~\ref{fig:glue} shows the improvement in cdec by changing the glue rule formulation. This improvement was the direct result of research comparing the three decoders.

 \begin{figure}[h]
 \begin{center}
 \input{1111-8/glue_model.tex}
 \end{center}
 \caption{Affect on model score by changing glue-rule formulation}
 \label{fig:glue}
 \end{figure}
>>>>>>> e417a6adcf4f1e49954836b14799509fecdea11c
